Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-11-09 fib2.tex
start on modular functors

\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{enumerate}

@@

We give an informal introduction to
anyonic topological quantum
field theory in $(2+1)$-dimensions.
See \cite{beverland2014} for a similar treatment.
Note that these theories give rise to
\emph{doubled} anyonic charges, and so
the Fibonacci example in the main text simulates
one half of such a system.

@@

We list the axioms for a \emph{2-dimensional unitary modular functor}
\cite{Turaev1994}, \cite{Walker1991}.

>>>>

\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{enumerate}
\usepackage{mathrsfs}

@@

%We give an informal introduction to
%anyonic topological quantum
%field theory in $(2+1)$-dimensions.
%See \cite{beverland2014} for a similar treatment.
%Note that these theories give rise to
%\emph{doubled} anyonic charges, and so
%the Fibonacci example in the main text simulates
%one half of such a system. % MEH!

@@

We list the axioms for a \emph{2-dimensional unitary topological modular functor}.
 % abbreviated as \emph{MF}.
For the details of this construction, see
\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2004.}

For our purposes a \emph{surface} will be an
oriented $2$-dimensional manifold with boundary.
Each boundary component is labelled with
an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
This is the set of ``anyon labels'', and comes
equiped with an involution $\hat{}$ such that $\hat{1}=1.$
Each boundary component is oriented (either explicitly or
otherwise by using the orientation of the manifold)
and contains a distinguished point.

We will mostly be concerned with \emph{planar} such
surfaces, ie. a disc with zero or more holes.

\newcommand{\F}{\mathscr{H}} % H or F ?

A modular functor $\F$ associates to every
surface $M$ a finite dimensional complex
vector space $\F(M)$, called the \emph{fusion space} of $M$.
A map of surfaces $f:M\to N$ will be understood to be
a topological homeomorphism that preserves boundary
labels and orientation, and
the modular functor assocates such an $f$ to a
unitary transformation $\F(f) : \F(M)\to\F(N).$
Functoriality requires that $\F$
respect composition of homeomorphisms.

We have the following axioms for $\F.$

{\bf Axiom I.}
The disjoint union of two surfaces $M$ and $N$ 
is assocated with
the tensor product of fusion spaces:
$$
    \F(M\amalg N) = \F(M)\otimes \F(N).
$$
This is natural from the point of view of quantum
physics, where the Hilbert space of two disjoint
systems is the tensor product of the space for
each system.

{\bf Axiom II.}
The fusion space of an empty surface is one dimensional: 
$\F(\phi) \cong \mathbb{C}.$

{\bf Axiom III.}
Gluing.
